Projit: An Open Source tool for Decoupled Data Science

### 2023-07-25 docs/paper/paper.tex
Fixing bug in CLI - updating references

\begin{abstract} 
Scientific practice has expanded to become increasingly dependent of digitial technologies,
large scale data processing and advanced analytical methods. These shifts have demanded new
methods of implementing and recording the details of scientific projects. Monolothic applications
have the advantage of a single and consistent design, however they impede the ability of users to
innovate and incrementally improve processes. We discuss the qualities of an ideal eScience framework
for building multi-stage collaboration scinetific workflows and present an open source implementation
for managing scientific processes in a decoupled fashion that permits both flexible implementation of
any stage of processing, and greater ease of meta-data analysis.
\end{abstract}

@@

Progress in scientific research depends heavily on accurate record keeping of previous
experimental approaches and results. Failure to maintain these records impedes progress
by making it difficult to reproduce work, or imposing the costs of repeatedly testing 
failed lines of experimentation. This cost becomes particularly high in the age of the
reproducibility crisis, as a many teams running the same experiments in parallel, without
knowledge of each others work, has produced a factory line of un-reproducible results.

@@

Projit has been implemented as python package that functions as both a command line application
and library that can be included inside other scripts and applications. The command line application
can be used to query the project metadata in much the same way that the git application can be used.
A user can add, modify and list the collection of data assets in the project: datasets, experiments 
and results are all accessible from the command line application.

The python package can be included in a script so that the script can access the project metadata store.
This allows the script to find the location of common datasets, register themselves as an experiment
and store results once the script is complete. Programmatic interaction with the project data through
the projit API is what permits the scripts of a project to be decoupled and contribute to the project
without being aware of how any other element is structured or implemented.

>>>>

\begin{abstract} 
Scientific practice has expanded to become increasingly dependent of digitial technologies,
large scale data processing and advanced analytical methods. These shifts have demanded new
methods of implementing and recording the details of scientific projects. Monolothic applications
have the advantage of a single and consistent design, however they impede the ability of users to
innovate and incrementally improve processes. We discuss the qualities of an ideal eScience framework
for building multi-stage collaboration scientific workflows and present an open source implementation
for managing data science processes in a decoupled fashion that permits both flexible implementation of
any stage of processing, and greater ease of meta-data analysis.
\end{abstract}

@@

Progress in scientific research depends heavily on accurate record keeping of previous
experimental approaches and results. Failure to maintain these records impedes progress
by making it difficult to reproduce work, or imposing the costs of repeatedly testing 
failed lines of experimentation. This cost becomes particularly high in the age of the
reproducibility crisis where many teams are running the same experiments in parallel, without
knowledge of each others work, and producing a factory line of un-reproducible results 
\cite{Ioannidis2005}.

@@

Projit has been implemented as python package that functions as both a command line application
and library that can be included inside other scripts and applications. The command line application
can be used to query the project metadata in much the same way that the git application can be used.
A user can add, modify and list the collection of analytical assets in the project: datasets, experiments 
parameters, tags and results are all accessible from the command line application.

The python package can be included in a script so that the script can access the project metadata store.
This allows the script to find the location of common datasets, register themselves as an experiment
and store results once the script is complete. Programmatic interaction with the project data through
the projit API is what permits the scripts of a project to be decoupled and contribute to the project
without being aware of how any other element is structured or implemented. Furthermore, as the metadata
is stored locally in standard JSON files, these can be stored inside a cloud repository and then contributed
to by collaborators. This allows distributed data science teams to define their own lines of experimentation,
but use a synchronised data set then continually contribute to a central meta-data store of project results.
